One-at-a-time Parameter Perturbation Ensemble of the Community Land Model, version 5.1

### 2025-04-02 ms/ms.tex
Updates from Overleaf

Understanding the range of outcomes arising from the many plausible parameter combinations is a critical step in robust uncertainty quantification. Parameter sensitivity tests can be used to gauge parametric uncertainty, and a collection of systematic parameter sensitivity tests across multiple parameters is often termed a Perturbed Parameter Ensemble (PPE, also referred to as Perturbed Physics Ensemble), with examples in the coupled \cite{murphy2004} and land-only contexts \cite{dagon2020,mcneall2024}. 
One important application of PPEs has been assessing uncertainty in climate model projections \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
Beyond uncertainty quantification, PPEs also form a basis for automated model calibration through various approaches like history matching \cite{williamson2013,williamson2017,hourdin2020,couvreux2021,mcneall2024} or Bayesian methods \cite{cleary2021}.
Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large PPEs \cite{qian2018}.
In a more general sense, PPEs yield a robust knowledge basis for understanding and working with a given climate model. This can aid in introducing new users to the model, or to help steer and facilitate model development.

The process of parameter estimation for the complex land models typically embedded within Earth System Models is challenging on account of the intrinsic complexity of the heterogeneous land surface, the diversity and plasticity of plant and microbial life, and the multiplicity of domains that comprise the terrestrial biosphere (e.g, hydrology, snow, biogeochemistry, physiology, land management, etc.). The number of model parameters required to represent all the relevant processes is large and model simulations are relatively expensive, presenting a major barrier to robust objective calibration, model interpretation, and development \cite{fisher2020,dagon2020}.
Thorough assessment of the parametric sensitivity of land models in a manner that is repeatable, open, and integrated with ongoing code development is desirable but challenging \cite{hourdin2017,balaji2022}. It typically requires extensive computational time,  software engineering, and domain-specific expert scientific knowledge. Our work here tries to alleviate each of these challenges in turn, at least within the context of one land model. While we are not yet at the point of automated calibration, we present herein several innovations that will serve to make an automated calibration system more technically feasible.

In this project we create a large PPE with the Community Land Model 5.1 with biogeochemistry configuration (CLM5.1-BGC, hereafter CLM)\cite{lawrence2019}. We extend the work of \citeA{dagon2020} which utilized a PPE to calibrate a subset of CLM parameters. Here we include a broader suite of parameters and continue to enhance the software tools for parameter perturbation and optimization. The goal of this project is to systematize the parameter perturbation process within the CLM modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across a wide range of land model processes. In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.
The dataset has already demonstrated utility for diagnosing parameter effects \cite{cheng2023,yan2023a,yan2023b,zarakas2024}, while the software and modeling infrastructure has greatly expanded our capability to generate insights about parameter effects and uncertainties within CLM.

@@

Identification of the complete parameter set of a land surface model is in itself a non-trivial exercise, as in practice, many empirical constants are hard-coded and not amenable to systematic perturbation \cite{mendoza2015,cuntz2016}. For the purposes of this activity, we identified a broad set of 211 CLM-BGC parameters, and enabled their modification via the model parameter file. Several domains were not perturbed, including crops, methane emissions, emissions of biogenic volatile organic compounds and dust, urban properties, and river flow parameters. The crop model was not utilized as our initial focus is on unmanaged land. Of the 211 parameters, 145 are scalar-valued, with a single parameter value acting globally. The remaining 66 parameters include a plant functional type (PFT) dimension, with the potential for different parameter values for each unique plant functional type. Not all parameters are currently utilizing this functionality, such as \textit{medlynintercept} where the default value is 100 $\mu$mol H$_2$O m$^{-2}$ s$^{-1}$ for all sixteen of CLM's natural vegetation PFTs.

\begin{landscape}
 \begin{table}[h]
 \caption{In total, 211 parameters were perturbed in this experiment. These are the parameters mentioned within the main text. A complete set of parameters, with ranges, is included in a spreadsheet in the supplementary information.}
 \centering
 \begin{tabular}{l l c}
 \hline
  Parameter  & Description & Model Domain \\
 \hline
cv & Turbulent transfer coefficient & Sensible, latent heat and momentum fluxes \\
dleaf & Leaf characteristic length & Sensible, latent heat and momentum fluxes \\
d\_max & Dry surface layer (DSL) parameter & Sensible, latent heat and momentum fluxes \\
frac\_sat\_soil\_dsl\_init & Fraction of saturated soil at which DSL initiates & Sensible, latent heat and momentum fluxes \\
fff & Decay factor for fractional saturated area & Hydrology \\
liq\_canopy\_storage\_scalar & Canopy-storage-of-liquid-water parameter & Hydrology \\
maximum\_leaf\_wetted\_fraction & Maximum leaf wetted fraction & Hydrology \\
sand\_pf & Perturbation factor for sand content of soil column & Hydrology \\
sucsat\_sf & Scale factor for minimum soil water potential & Hydrology \\
medlynintercept & Medlyn intercept of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
medlynslope & Medlyn slope of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
tpu25ratio & Ratio of tpu25top to vcmax25top & Stomatal resistance and photosynthesis \\
jmaxb0 & Baseline proportion of nitrogen allocated for electron transport & Photosynthetic capacity\\
jmaxb1 & Response of electron transport rate to light & Photosynthetic capacity\\
slatop & Specific leaf area at top of canopy & Photosynthetic capacity\\
theta\_cj & empirical curvature parameter for photosynthesis colimitation& Photosynthetic capacity \\
wc2wjb0 & Baseline ratio of wc:wj & Photosynthetic capacity \\
FUN\_fracfixers & fraction of carbon available for N fixation & Fixation and uptake of Nitrogen \\
KCN & Nitrogen acquisition parameter group & Fixation and uptake of Nitrogen \\
kmax & Plant segment max conductance & Plant hydraulics \\
krmax & Root segment max conductance & Plant hydraulics \\
psi50 & Water potential at 50\% loss of conductance & Plant hydraulics \\
nstem & Stem number & Biomass heat storage \\
lmr\_intercept\_atkin & Intercept in the calculation of leaf maintenance respiration& Plant respiration \\
froot\_leaf & Allocation parameter: new fine root C per new leaf C & Carbon and nitrogen allocation \\
leafcn & Leaf C:N & Carbon and nitrogen allocation \\
leaf\_long & Leaf longevity & Vegetation phenology and turnover \\
cpha & Activation energy for cp & Acclimation parameters \\
jmaxhd & Deactivation energy for jmax & Acclimation parameters \\
kcha & Activation energy for kc & Acclimation parameters \\
lmrha & Activation energy for lmr & Acclimation parameters \\
lmrhd & Deactivation energy for lmr & Acclimation parameters \\
tpuha & Activation energy for tpu & Acclimation parameters \\
tpuse\_sf & Scale factor for tpu entropy term & Acclimation parameters \\
vcmaxha & Activation energy for vcmax & Acclimation parameters \\
vcmaxhd & Deactivation energy for vcmax & Acclimation parameters \\
 \hline
 \end{tabular}
 \end{table}
\end{landscape}

@@

In one case, a significant CLM bug was identified after the completion of our primary experiment (\url{https://github.com/ESCOMP/CTSM/issues/2120}). Namely that the values for two nitrogen uptake parameters had been transposed in \citeA{brzostek2014}. Resolving the issue resulted in an approximately 5\% decrease in gross primary production of (Supp Figure S4) in the control simulations, and also significantly altered the size of the various parameter effects. Any PPE should be seen as intrinsically connected to its underlying codebase (bugs and all), and, reflecting this, we did not rerun the rest of the PPE. Therefore the majority of simulations contain the erroneous parameter values, and may slightly overestimate GPP. The bug has since been resolved in later model versions.

@@

This model configuration allowed for over 2000 simulations across our six forcing scenarios.
Overall, we found substantial impacts of parametric uncertainty on model behavior, in some cases exceeding the magnitude of scenario effects (Figure \ref{fig:ranges}). In the control scenario, the global sum of gross primary production (GPP) ranged from 103 to 158 PgC per year across all ensemble members, and net ecosystem production (NEP) ranged from 1.7 to 3.8 PgC per year. NEP was especially variable in the high CO$_2$ scenario, varying from 1.6 to 5.7 PgC per year. One perturbation, reducing the heat capacity of sand by 20\%, proved destructive in the future climate scenario, resulting in inhospitably hot soil conditions and widespread plant death. A perturbation of $\pm$20\% may exceed the reasonable range for this parameter, but this simulation was instructive for exposing the model's response to hot soils. Carrying out an extensive PPE increases the possibility of exposing unexpected model behavior, including unforeseen tipping points, brittle parameterizations, and/or bugs.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/ranges.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across six forcing scenarios. Circles mark the CLM5.1 default simulation, and the bars span the ensemble ranges generated by individual parameter perturbations.}
\label{fig:ranges}
\end{figure}

@@

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise land models \cite{kattge2020}. Even with parameters that have an empirical basis from field studies, uncertainty quantification is difficult to the scale mismatch between site-level observations and land model grid cells \cite{liu2021}. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.

@@

For this experiment we opted for a one-at-a-time perturbation strategy, testing a minimum and maximum value for each parameter. We found that parameter effects could be quite large, in some cases exceeding the effects of our forcing scenarios (Figure \ref{fig:ranges}). That said, the majority of parameter perturbations had small effects for any specific model variable or metric, such that a majority of simulations were clustered around the default simulation. In the case of canopy evaporation, for example, more than 95\% of the ensemble variance could be explained by the ten most influential parameters (Figure \ref{fig:variance}). This indicates that there may be tractable parameter estimation sub-problems if global calibration of all 211 parameters proves infeasible.

@@

A one-at-a-time PPE cannot capture parameter interactions, and our min/max sampling protocol precludes diagnosing non-linearities. As such, this dataset will be insufficient for most calibration activities or for estimating overall parametric uncertainty. A primary utility of our dataset is that we can diagnose parameter effects without the uncertainty contributed by an emulator or a regression model. As such, it is easy to diagnose which parameters are most influential on a given process. We have published a large set of ensemble diagnostic plots online, which serves as a valuable enhancement to our model technical documentation. Now, in addition to seeing the definition of a given parameter, and the relevant equations, a model user can easily investigate the magnitude and spatial patterns of its effects (e.g. Figure \ref{fig:map}). This could be useful for investigating obvious model deficiencies, such as regional LAI biases, or to understand potential model responses under different forcing scenarios (e.g. plant survival under low CO$_2$ conditions).

>>>>

Understanding the range of outcomes arising from the many plausible parameter combinations is a critical step in robust uncertainty quantification. Parameter sensitivity tests can be used to gauge parametric uncertainty, and a collection of systematic parameter sensitivity tests across multiple parameters is often termed a Perturbed Parameter Ensemble (PPE, also referred to as Perturbed Physics Ensemble), with examples in the coupled \cite{murphy2004} and land-only contexts \add{zqzbaker2022} \cite{dagon2020,mcneall2024}. 
One important application of PPEs has been assessing uncertainty in climate model projections \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
Beyond uncertainty quantification, PPEs also form a basis for automated model calibration through various approaches like history matching, \add{which does not require assumptions regarding parameter distributions} \cite{williamson2013,williamson2017,hourdin2020,couvreux2021,mcneall2024}, or Bayesian methods \add{zqz zeihn2012,fer2018} \cite{cleary2021}, \add{or using genetic algorithms zqz bastrikov2018}.
Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large PPEs \cite{qian2018}.
In a more general sense, PPEs yield a robust knowledge basis for understanding and working with a given climate model. This can aid in introducing new users to the model, or to help steer and facilitate model development.

The process of parameter estimation for the complex land models typically embedded within Earth System Models is challenging on account of the intrinsic complexity of the heterogeneous land surface, the diversity and plasticity of plant and microbial life, and the multiplicity of domains that comprise the terrestrial biosphere (e.g, hydrology, snow, biogeochemistry, physiology, land management, etc.). The number of model parameters required to represent all the relevant processes is large and model simulations are relatively expensive, presenting a major barrier to robust \remove{objective} calibration, model interpretation, and development \cite{fisher2020,dagon2020}.
Thorough assessment of the parametric sensitivity of land models in a manner that is repeatable, open, and integrated with ongoing code development is desirable but challenging \cite{hourdin2017,balaji2022}. It typically requires extensive computational time,  software engineering, and domain-specific expert scientific knowledge. Our work here tries to alleviate each of these challenges in turn, at least within the context of one land model. While we are not yet at the point of automated calibration, we present herein several innovations that will serve to make an automated calibration system more technically feasible.

In this project we create a large PPE with the Community Land Model 5.1 with biogeochemistry configuration (CLM5.1-BGC, hereafter CLM)\cite{lawrence2019}. We extend the work of \citeA{dagon2020} which utilized a PPE to calibrate a subset of CLM parameters. Here we include a broader suite of parameters and continue to enhance the software tools for parameter perturbation and optimization. The goal of this project is to systematize the parameter perturbation process within the CLM modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across a wide range of land model processes. In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.
The dataset has already demonstrated utility for diagnosing parameter effects \cite{cheng2023,yan2023a,yan2023b,zarakas2024}, while the software and modeling infrastructure has greatly expanded our capability to generate insights about parameter effects and \remove{uncertainties} \add{sensitivities} within CLM.

@@

Identification of the complete parameter set of a land surface model is in itself a non-trivial exercise, as in practice, many empirical constants are hard-coded and not amenable to systematic perturbation \cite{mendoza2015,cuntz2016}. For the purposes of this activity, we identified a broad set of 211 CLM-BGC parameters, and enabled their modification via the model parameter file. Several domains were not perturbed, including crops, methane emissions, emissions of biogenic volatile organic compounds and dust, urban properties, and river flow parameters. The crop model was not utilized as our initial focus is on unmanaged land. Of the 211 parameters, 145 are scalar-valued, with a single parameter value acting globally. The remaining 66 parameters include a plant functional type (PFT) dimension, with the potential for different parameter values for each unique plant functional type. \add{For any given PFT parameter, all PFTs were perturbed in tandem (i.e. all 16 PFTs to their maximum values and then to their minimum values), but with potentially different ranges for each PFT. Explicit parameter ranges for each parameter (and each PFT) are provided in a supplemental spreadsheet.} \remove{Not all parameters are currently utilizing this functionality, such as \textit{medlynintercept} where the default value is 100 $\mu$mol H$_2$O m$^{-2}$ s$^{-1}$ for all sixteen of CLM's natural vegetation PFTs.}

\begin{landscape}
 \begin{table}[h]
 \caption{In total, 211 parameters were perturbed in this experiment. These are the parameters mentioned within the main text. A complete set of parameters, with ranges, is included in a spreadsheet in the supplementary information.}
 \centering
 \begin{tabular}{l l c c}
 \hline
  Parameter  & Description & Model Domain & Varies by PFT? \\
 \hline
cv & Turbulent transfer coefficient & Sensible, latent heat and momentum fluxes & \\
dleaf & Leaf characteristic length & Sensible, latent heat and momentum fluxes & yes \\
d\_max & Dry surface layer (DSL) parameter & Sensible, latent heat and momentum fluxes &\\
frac\_sat\_soil\_dsl\_init & Fraction of saturated soil at which DSL initiates & Sensible, latent heat and momentum fluxes &\\
fff & Decay factor for fractional saturated area & Hydrology &\\
liq\_canopy\_storage\_scalar & Canopy-storage-of-liquid-water parameter & Hydrology &\\
maximum\_leaf\_wetted\_fraction & Maximum leaf wetted fraction & Hydrology &\\
sand\_pf & Perturbation factor for sand content of soil column & Hydrology &\\
sucsat\_sf & Scale factor for minimum soil water potential & Hydrology &\\
medlynintercept & Medlyn intercept of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis &yes\\
medlynslope & Medlyn slope of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis &yes\\
tpu25ratio & Ratio of tpu25top to vcmax25top & Stomatal resistance and photosynthesis &\\
jmaxb0 & Baseline proportion of nitrogen allocated for electron transport & Photosynthetic capacity&\\
jmaxb1 & Response of electron transport rate to light & Photosynthetic capacity&\\
slatop & Specific leaf area at top of canopy & Photosynthetic capacity&yes\\
theta\_cj & Empirical curvature parameter for photosynthesis colimitation& Photosynthetic capacity &yes\\
wc2wjb0 & Baseline ratio of wc:wj & Photosynthetic capacity &\\
FUN\_fracfixers & fraction of carbon available for N fixation & Fixation and uptake of Nitrogen &yes\\
KCN & Nitrogen acquisition parameter group & Fixation and uptake of Nitrogen &yes\\
kmax & Plant segment max conductance & Plant hydraulics &yes\\
krmax & Root segment max conductance & Plant hydraulics &yes\\
psi50 & Water potential at 50\% loss of conductance & Plant hydraulics &yes\\
nstem & Stem number & Biomass heat storage &yes\\
lmr\_intercept\_atkin & Intercept in the calculation of leaf maintenance respiration& Plant respiration &yes\\
froot\_leaf & Allocation parameter: new fine root C per new leaf C & Carbon and nitrogen allocation &yes\\
leafcn & Leaf C:N & Carbon and nitrogen allocation &yes\\
leaf\_long & Leaf longevity & Vegetation phenology and turnover &yes\\
cpha & Activation energy for cp & Acclimation parameters &\\
jmaxhd & Deactivation energy for jmax & Acclimation parameters &\\
kcha & Activation energy for kc & Acclimation parameters &\\
lmrha & Activation energy for lmr & Acclimation parameters &\\
lmrhd & Deactivation energy for lmr & Acclimation parameters &\\
tpuha & Activation energy for tpu & Acclimation parameters &\\
tpuse\_sf & Scale factor for tpu entropy term & Acclimation parameters &\\
vcmaxha & Activation energy for vcmax & Acclimation parameters &\\
vcmaxhd & Deactivation energy for vcmax & Acclimation parameters &\\
 \hline
 \end{tabular}
 \end{table}
\end{landscape}

@@

In one case, a significant CLM bug was identified after the completion of our primary experiment (\url{https://github.com/ESCOMP/CTSM/issues/2120}). Namely that the values for two nitrogen uptake parameters had been transposed in \citeA{brzostek2014}. Resolving the issue resulted in an approximately 5\% decrease in gross primary production of (Supp Figure S4) in the control simulations, and also significantly altered the size of the various parameter effects. Any PPE should be seen as intrinsically connected to its underlying codebase (bugs and all), and, reflecting this, we did not rerun the rest of the PPE. Therefore the majority of simulations contain the erroneous parameter values, and may slightly overestimate GPP. \add{The interacting effect of this bug fix with all of the other parameter perturbations was not explored.} The bug has since been resolved in later model versions \add{and will be tested in future PPEs}.

@@

This model configuration allowed for over \remove{2000} \add{2500} simulations across our six forcing scenarios.
Overall, we found substantial impacts of parametric \remove{uncertainty} \add{sensitivity} on model behavior, in some cases exceeding the magnitude of scenario effects (Figure \ref{fig:ranges}). In the control scenario, the global sum of gross primary production (GPP) ranged from 103 to 158 PgC per year across all ensemble members, and net ecosystem production (NEP) ranged from 1.7 to 3.8 PgC per year. NEP was especially variable in the high CO$_2$ scenario, varying from 1.6 to 5.7 PgC per year. One perturbation, reducing the heat capacity of sand by 20\%, proved destructive in the future climate scenario, resulting in inhospitably hot soil conditions and widespread plant death. A perturbation of $\pm$20\% may exceed the reasonable range for this parameter, but this simulation was instructive for exposing the model's response to hot soils. Carrying out an extensive PPE increases the possibility of exposing unexpected model behavior, including unforeseen tipping points, brittle parameterizations, and/or bugs.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/main/ranges.png}
\caption{\add{Global annual mean values for the default simulations (circles) and ensemble ranges (bars) for} (a) gross primary production (GPP), (b) net ecosystem production (NEP), \add{(c) leaf area index (LAI), and (d) evapotranspiration (ET)} across six forcing scenarios. \add{(e) Global LAI across the full set of parameter perturbation simulations under the future climate scenario. Most simulations fall within 5\% of the default LAI, with a small number of parameters generating larger effects. One perturbation, reducing sand heat capacity by 20\% caused a very low LAI.} \remove{Circles mark the CLM5.1 default simulation, and the bars span the ensemble ranges generated by individual parameter perturbations.}}
\label{fig:ranges}
\end{figure}

@@

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise land models \cite{kattge2020}. Even with parameters that have an empirical basis from field studies, uncertainty quantification is difficult due to the scale mismatch between site-level observations and land model grid cells zqz \cite{liu2021}. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.

@@

For this experiment we opted for a one-at-a-time perturbation strategy, testing a minimum and maximum value for each parameter. We found that parameter effects could be quite large, in some cases exceeding the effects of our forcing scenarios (Figure \ref{fig:ranges}). That said, the majority of parameter perturbations had small effects for any specific model variable or metric, such that a majority of simulations were clustered around the default simulation (Figure \ref{fig:ranges}e). In the case of canopy evaporation, for example, more than 95\% of the ensemble variance could be explained by the ten most influential parameters (Figure \ref{fig:variance}). This indicates that there may be tractable parameter estimation sub-problems if global calibration of all 211 parameters proves infeasible.

@@

A one-at-a-time PPE cannot capture parameter interactions, and our min/max sampling protocol precludes diagnosing non-linearities. As such, this dataset will be insufficient for most calibration activities or for estimating overall parametric uncertainty. A primary utility of our dataset is that we can diagnose parameter effects without the uncertainty contributed by an emulator or a regression model. As such, it is easy to diagnose which parameters are most influential on a given process. We have published a large set of ensemble diagnostic plots online \add{(url:}\url{https://webext.cgd.ucar.edu/I2000/PPEn11_OAAT/}\add{)}, which serves as a valuable enhancement to our model technical documentation. Now, in addition to seeing the definition of a given parameter, and the relevant equations, a model user can easily investigate the magnitude and spatial patterns of its effects (e.g. Figure \ref{fig:map}). This could be useful for investigating obvious model deficiencies, such as regional LAI biases, or to understand potential model responses under different forcing scenarios (e.g. plant survival under low CO$_2$ conditions).
